\plaintitle

### 2017-01-08 drafts/labor/complexity.tex
complexity negativity

So, in the case of complexity, the history of piecework does not yet offer compelling evidence that on--demand work will achieve far more complex outcomes. 
It will be far more broadly distributed---reaching many more tasks and areas of expertise by virtue of the internet---but not necessarily far more complex than what piecework previously achieved.

>>>>

So, in the case of complexity, the history of piecework does not yet offer compelling evidence that on--demand work will achieve far more complex outcomes than it has today.
Improvements in workflows, measurement and evaluation have already been made, and it is not clear that the remaining challenges are readily solveable.
On--demand work will be far more broadly distributed than piecework historically was---reaching many more tasks and areas of expertise by virtue of the internet---but not necessarily far more complex than what piecework previously achieved.
